
%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,letterpaper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\PassOptionsToPackage{unicode,final}{hyoerref} 
% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
\usepackage{pifont}
% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
%\usepackage[scale=0.80]{geometry}
\usepackage[left=2cm,right=1.5cm,top=2cm,bottom=1.5cm]{geometry}

\setlength{\hintscolumnwidth}{3.3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{B.Sc.}{Juan Sebasti\'an\\[15pt] Castellanos-Dur\'an}
%\name{}{Juan Sebasti\'an\\[15pt] Castellanos-Dur\'an}
\title{Curriculum Vitae}                               % optional, remove / comment the line if not wanted
% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+57~312~314~2506}                   % optional, remove / comment the line if not wanted
\phone[fixed]{+57~(1)~244~9585}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{jsebastian405@gmail.com}                              
\address{Cll 26  N\textsuperscript{o} 40-77 Edificio Junio APTO 201}{111321}{Bogot\'a D.C. Colombia}
%\email{jsebastian405@gmail.com}                               % optional, remove / comment the line if not wanted
%\homepage{www.johndoe.com}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[120pt][0.6pt]{Foto_me3.jpg}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted
%\usepackage{hyperref}
%\usepackage[hidelinks]{hyperref}


% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS
\usepackage{array}
\renewcommand*{\cvitem}[3][.25em]{%
  \begin{tabular}{@{}p{\hintscolumnwidth}@{\hspace{\separatorcolumnwidth}}p{\maincolumnwidth}@{}}%
      \raggedleft\hintstyle{#2} &{#3}%
  \end{tabular}%
  \par\addvspace{#1}}
% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------http://solar-center.stanford.edu/IRIS/SummerProgram/------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Profile}
As a young researcher interested in astrophysics and its applications, especially in those related to solar physics, I have acquired excellent physics concepts and tools, such as, data analysis, computer programming, experimental techniques, and a logical-mathematical way of thinking.  In addition, I have developed linguistic (English, German), observational (telescopes) skills and data analysis (IDL-SSW). All of those tools and skills are essential to do research in the fields of astronomy and solar physics.
Therefore, the devotion to the research, responsibility, creativity, autonomy to develop research projects and team work are a priority for me. 

\section{Education}
\cvitem{Ago 2014 - present}{\textbf{Graduate student - Master of Science in Astronomy}}
\cvitem{}{Observatorio Astron\'omico Nacional}
\cvitem{}{Universidad Nacional de Colombia, Bogot\'a - Colombia}
\medskip
\cvitem{2008 - 2013}{\textbf{Bachelor of Science in Physics}}
\cvitem{}{Five years program - Graduation April 23, 2014}
\cvitem{}{Universidad Nacional de Colombia, Bogot\'a - Colombia} 
\cvitem{G.P.A.}{4.1/5.0}
\cvitem{Senior thesis}{\emph{\textbf{Study of the excess in White-Light during Solar Flares via the Backwarming model}}}
\cvitem{Supervisor}{Benjam\'{i}n Calvo-Mozo}
\cvitem{}{ Observatorio Astron\'omico Nacional - Universidad Nacional de Colombia, Colombia}
\cvitem{External}{Juan Carlos Martínez Oliveros}
\cvitem{advisor}{Space Sciences Laboratory - University of California, Berkeley. CA, U.S.A.}

%\cvitem{Abstract}{
%We studied 43 White-light flares (WLF) using the satellite data from the Solar Dynamic Observatory concluding that the applied methods on the study of these processes generate artefacts which produce flux overestimation during WLFs. At this point, we proposed a new method which achieves considerable progress respect to classical methods. In addition, we analysed the WLFs writing a radiative transfer code to simulate the $H^-$ ion emission and the opacities of H, Si, C concluding that the Backwarming model is able to heat the lower solar atmosphere to produce the white-light emission.}

\section{Academic Experience: Schools, Workshops and Seminars}
\cvitem{Dec 8-12, 2014}{\href{http://departamentodefisicaeventos.epn.edu.ec/}{\textbf{Participant}, Primera Escuela Andina de Astronom\'{i}a y Astrof\'{i}sica: Visi\'on Moderna de la Cosmolog\'{i}a (EAAA).}}
\cvitem{}{Escuela Polit\'ecnica Nacional. Quito, Ecuador}
%\cvitem{}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{Aug 25-Sep 5, 2014}{\href{http://xilonen.inaoep.mx/~progharo/gh2014School/}{\textbf{Participant \& LOC}, Guillermo Haro 2014: Advanced School on Integral Field Spectroscopy Techniques and Analysis.}}
\cvitem{}{Instituto Nacional de Astrof\'{i}sica, \'{O}ptica y Electr\'onica - INAOE. Puebla, Mexico}
%\cvitem{}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{Jun 17-Aug 23, 2014}{\textbf{Summer Internship in Astrophysics and Astronomical Instrumentation at INAOE}}
\cvitem{}{Instituto Nacional de Astrof\'{i}sica, \'{O}ptica y Electr\'onica - INAOE. Puebla, Mexico}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\cvitem{2013 - 2014}{\textbf{Book - Editor's assistant}, Astronom\'{i}a para todos. Retos modernos de una ciencia milenaria. Editor Benjam\'{i}n Calvo-Mozo - 19 Authors. \textbf{ISBN 978-958-761-656-9}}
\cvitem{}{Observatorio Astronomico Nacional - Universidad Nacional de Colombia}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{Jun 24-Aug 30, 2013}{\href{http://solar-center.stanford.edu/IRIS/SummerProgram/}{\textbf{The 2013 IRIS Student Summer Intern Research Program}}}
\cvitem{}{Stanford University and Lockheed Martin Solar and Astrophysics Laboratory. CA, U.S.A.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{Jul 2 - 21, 2012}{\href{http://www.observatorio.unal.edu.co/eventos/solarschool/}{\textbf{International Summer School – Solar Astrophysics: Modern Trends and Techniques}}}
\cvitem{}{Observatorio Astronomico Nacional - Universidad Nacional de Colombia}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{May 28 - 1, 2012}{\href{http://matematicas.uniandes.edu.co/~cursillo_gr/escuela2012/}{\textbf{Fourth School in Physical Mathematics: Quantum Integrable Systems}}}
\cvitem{}{Universidad de los Andes. Bogot\'a, Colombia}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{Sept 12 - 16, 2011}{\href{http://www.ciencias.unal.edu.co/workshopstatisticalphysics/}{\textbf{First Workshop on Statistical Physics}}}
\cvitem{}{Universidad de los Andes and Universidad Nacional de Colombia}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{Aug 9 - 11, 2010}{\href{http://www.observatorio.unal.edu.co/eventos/pasados/cocoa/escuela.html}{\textbf{Extragalactic Astronomy School}}}
\cvitem{}{Observatorio Astronomico Nacional - Universidad Nacional de Colombia}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\cvitem{2012 -2013}{\textbf{Graduate Courses attended}: Astrophysics, Observational techniques in astronomy, Stellar structure, Select Topics in astronomy teaching.}
%\cvitem{}{Observatorio Astronomico Nacional - Universidad Nacional de Colombia}
%\cvitem{}{Bogot\'a, Colombia}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage %AAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAA
\section{Conferences, Presentations, Posters \& Proceedings}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{May 25-28, 2015}{\href{http://spg.iaa.es/Workshop}{\textbf{Contributed Talk}}, Vector magnetic field changes during flares using SDO/HMI data.}
\cvitem{2015}{\texttt{J.S. Castellanos-Dur\'an, L. Kleint \& B. Calvo-Mozo.}}
\cvitem{}{3rd SOLARNET Workshop: ``Polarization in the Sun, the Solar System, and Beyond''}
\cvitem{}{Granada, España}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{Dec 1 - 5 2014}{\href{http://aulavirtual.udenar.edu.co/cocoa/}{\textbf{Contributed Talk and proceedings}}, \href{http://aulavirtual.udenar.edu.co/cocoa/wp-content/uploads/2014/12/Resumenes-IV-COCOA-2014.pdf}{El modelo del Backwarming y un nuevo método observacional para entender los flares que emiten luz blanca} }
\cvitem{}{\texttt{J.S. Castellanos-Dur\'an,  \& B. Calvo-Mozo.}}
\cvitem{}{IV Congreso Colombiano de Astronom\'{i}a y Astrof\'{i}sica (COCOA 2014) - Universidad de Nariño. March, 2015. Vol 6 No. 1-2 FACIEN.  ISBN 2256-3830}
%\cvitem{}{Pasto, Colombia.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{Dec 1 - 5 2014}{\href{http://aulavirtual.udenar.edu.co/cocoa/}{\textbf{Contributed Talk and proceedings}}, \href{http://aulavirtual.udenar.edu.co/cocoa/wp-content/uploads/2014/12/Resumenes-IV-COCOA-2014.pdf}{Cambios tipo Heaviside durante flares: Análisis de la componete en la línea de la visual y el vector campo magnético} }
\cvitem{}{\texttt{J.S. Castellanos-Dur\'an, L. Kleint \& B. Calvo-Mozo.}}
\cvitem{}{IV Congreso Colombiano de Astronom\'{i}a y Astrof\'{i}sica (COCOA 2014) - Universidad de Nariño. March, 2015. Vol 6 No. 1-2 FACIEN. ISBN 2256-3830}
%\cvitem{}{Pasto, Colombia.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{Dec 1 - 5 2014}{\href{http://aulavirtual.udenar.edu.co/cocoa/}{\textbf{Contributed Talk and proceedings}}, \href{http://aulavirtual.udenar.edu.co/cocoa/wp-content/uploads/2014/12/Resumenes-IV-COCOA-2014.pdf}{¿Qu\'e sabemos de las galaxias?: comparaci\'on de propiedades integradas vs. espacialmente
resueltas usando espectroscop\'{i}a de campo integral} }
\cvitem{}{\texttt{J.S. Castellanos-Dur\'an,  \& F.F. Rosales-Ortega}}
\cvitem{}{IV Congreso Colombiano de Astronom\'{i}a y Astrof\'{i}sica (COCOA 2014) - Universidad de Nariño. March, 2015. Vol 6 No. 1-2 FACIEN.  ISBN 2256-3830}
%\cvitem{}{Pasto, Colombia.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{Jun 9 - 13, 2014}{\textbf{Poster}, White-Light Flares: A proposed improvement to known classic reduction methods.}
\cvitem{}{\texttt{J. S. Castellanos-Dur\'an, J.D. Alvarado-Gomez, W. G. Fajardo-Mendieta \& B. Calvo-Mozo}}
\cvitem{}{Cambridge Workshop on Cool Stars, Stellar Systems, and the Sun ``CoolStars 18''. U.S.A.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{Aug 30, 2013}{\textbf{Poster}, Cluster analysis for two solar physics problems: Stokes parameters \& NUV spectra.}
\cvitem{}{\texttt{J. S. Castellanos-Dur\'an \& L. Kleint.}}
\cvitem{}{The 2013 IRIS Student Summer Intern Research Program - Stanford University and Lockheed Martin Solar and Astrophysics Laboratory. Palo Alto - CA, U.S.A.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{Nov 27 - 2, 2012}{\href{http://hessi.ssl.berkeley.edu/petaluma/program_wg3.shtml}{\textbf{Contributed Talk}, Characterization of white light, SXR and HXR kernels emissions in white light flares observed by SDO/HMI and RHESSI.}}
\cvitem{}{\texttt{J.S. Castellanos-Dur\'an, J.D. Alvarado-Gomez \& B. Calvo-Mozo.}}
\cvitem{}{12$^{th}$ RHESSI Workshop: Solar in Sonoma. Tracing the Connections in Solar Eruptive Events. University of California, Berkeley - NASA. Petaluma - CA, U.S.A.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{Dec 3 - 7, 2012}{\href{http://fallmeeting.agu.org/2012/eposters/eposter/sh43b-2162/}{\textbf{Poster}, Characterization of white light, SXR and HXR kernels emissions in white light flares observed by SDO/HMI and RHESSI.}}
\cvitem{}{\texttt{J.S. Castellanos-Dur\'an, J.D. Alvarado Gomez, J.C. Martinez Oliveros, J.C. Buitrago-casas, Benjamin Calvo-Mozo.}}
\cvitem{}{American Geophysical Union - AGU Fall Meeting. San Francisco - CA, U.S.A.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{Jul 2 - 21, 2012}{\textbf{Poster}, Study of the white light and hard X-rays emission of the M6.6 class flare of February 18 2011 using SDO/HMI and RHESSI.}
\cvitem{}{\texttt{J. S. Castellanos-Dur\'an, J. D. Alvarado-Gom\'ez, J.C. Mart\'{i}nez Oliveros \& B. Calvo-Mozo.}}
\cvitem{}{International Summer School in Solar Astrophysics: Modern Trends and Techniques}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{Aug 29 - 31, 2012}{\href{http://www.enid.unal.edu.co/2012/programa/detallado.html\#miercoles}{\textbf{Contributed Talk and proceedings}}, \href{http://www.enid.unal.edu.co/2012/memorias/fscommand/investigacion/40.pdf}{Caracterizaci\'on de la emisi\'on en luz blanca y en rayos-X de la fulguraci\'on GOES M6.6 del 18 de Febrero de 2011 usando SDO y RHESSI.} }
\cvitem{}{\texttt{J.S. Castellanos-Dur\'an, J.D. Alvarado-Gomez \& B. Calvo-Mozo.}}
\cvitem{}{Encuentro Nacional de investigaci\'on y desarrollo National (ENID 2012)} 
\cvitem{}{ISBN 978-958-761-308-7 - Universidad Nacional de Colombia.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage %AAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAA

\cvitem{Dec 5 - 9, 2011}{\href{https://fallmeeting.agu.org/2011/}{\textbf{Poster}, Observational Analysis of Photospheric Magnetic Field Restructuring During Energetic Solar Flares.}}
\cvitem{}{\texttt{J.D. Alvarado, J.S. Castellanos, J.C. Buitrago, J.C. Mart\'{i}nez, C.Lindsey, W.P. Abbett \& G.H. Fisher.}}
\cvitem{}{American Geophysical Union - AGU Fall Meeting 2012. San Francisco - CA, U.S.A.}
%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{Aug 3 - 6, 2010}{\textbf{Attended}, II Congreso Colombiano de Astronom\'{i}a y Astrof\'{i}sica (COCOA 2010)}
\cvitem{}{Observatorio Astronomico Nacional - Universidad Nacional de Colombia.}
\section{Languages}
\cvitemwithcomment{Spanish}{Mother tongue}{}
\cvitemwithcomment{English}{C1}{Perfect reading, listening and conversationally fluent}
\cvitemwithcomment{German}{A2}{Learning}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Computer skills}
\cvitem{Basic}{Operative systems (Linux, Mac OS, Windows)}
\cvitem{Intermediate}{\LaTeX, Beamer, OpenOffice, Office.}
\cvitem{Advanced}{IDL, SSWIDL, Python, IRAF, Mathematica.}

%\section{External Interests}
%\cvdoubleitem{}{\ding{44} Theater}{}{\ding{44} Tennis}
%\section{Miscellaneous}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\cvitem{2010-Present}{\textbf{Member}, Group of Solar Astrophysics (GoSA)}
%\cvitem{}{Observatorio Astronomico Nacional - Universidad Nacional de Colombia}
%\cvitem{}{Bogot\'a, Colombia}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\cvitem{2012 - 2013}{\textbf{Student assistantship} at Observatorio Astronomico Nacional}
%\cvitem{}{Universidad Nacional de Colombia}
%\cvitem{}{Bogot\'a, Colombia}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\cvitem{2012 - 2013}{\textbf{Member}, Sofisma Theater Studio group.}
%\cvitem{}{Bogot\'a, Colombia}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\cvitem{Oct 11 - 17}{\textbf{Participant}, XII National Festival of university theater. ASCUN CULTURA.}
%\cvitem{}{Universidad Autonoma del Caribe}
%\cvitem{}{Barranquilla, Colombia.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\cvitem{2009 - 2010}{\textbf{Member},Experimental theater group of National University.}
%\cvitem{}{Universidad Nacional de Colombia}
%\cvitem{}{Bogot\'a, Colombia}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\cvitem{Jan 29 - 06}{\textbf{Participant}, Second World Meeting of Youth Theater EMTIJ Chile.}
%\cvitem{2007}{Universidad de Artes y Ciencias Sociales ARCIS.}
%\cvitem{}{Santiago de Chile, Chile.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\cvitem{2000 - 2007}{\textbf{Member}, AMSA Theater group.}
%\cvitem{}{Bogot\'a, Colombia}
\section{References}
\cvitem{\textbf{Benjam\'{i}n}}{\textbf{Associate Professor, Observatorio Astronómico Nacional (OAN)}.}
\cvitem{\textbf{Calvo-Mozo}}{Universidad Nacional de Colombia, Bogotá - Colombia.}
\cvitem{}{bcalvom@unal.edu.co}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\cvitem{\textbf{Fabi\'an }}{\textbf{Tenure track Researcher, Instituto Nacional de Astrof\'{i}sica \'{O}ptica y Electr\'onica }}
\cvitem{\textbf{Rosales}}{Puebla, Mexico}
\cvitem{\textbf{Ortega}}{frosales@inaoep.mx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{\textbf{Julian David}}{\textbf{Ph.D. Student, European Southern Observatory (ESO)}.}
\cvitem{\textbf{Alvarado}}{Munich, Germany}
\cvitem{\textbf{G\'omez}}{jalvarad@eso.org }
% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}

\end{document}

\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%\clearpage
%-----       letter       ---------------------------------------------------------


%% end of file `template.tex'.
